Boutiques: a flexible framework for automated application integration in computing platforms

### 2017-11-07 boutiquespaper.tex
Rewrote abstract

\begin{abstract}Integrating applications in execution platforms such as web
  portals and workflow engines is critical to enable their sharing
  among scientific communities and their efficient execution on
  computing infrastructures. However, application integration remains
  a costly human effort that consists of 1)~installing the application
  on the target infrastructure, 2)~describing the application in a
  format compatible with the execution platform, and 3)~generating
  proper user interfaces. Application integration efforts are often
  replicated several times while interoperability would improve the
  quality of the integrations. We present \boutiques, a descriptive
  framework and command line utility to automatically import and
  exchange applications across platforms. \boutiques adopts a rich,
  flexible application description format that relies on Linux
  container environments Docker and Singularity to install
  applications across platforms in a lightweight manner. \boutiques is
  currently used by several distinct virtual research platforms, and
  has been used to describe dozens of applications in the
  neuroinformatics domain.
\end{abstract}

@@

Platforms such as web services, portals, scientific gateways, workflow
engines and virtual research environments commonly integrate
third-party applications to enable data processing on various types of
computing resources. Such applications, however, are often manually
and repeatedly integrated in different platforms whereas automating
and sharing this effort would improve computational
reproducibility~\cite{peng2011reproducible,Stodden1240} and contribute to Open
Science. Meanwhile, software container systems such as
Docker\footnote{\url{https://www.docker.com}} and
Singularity~\cite{kurtzer2017singularity} have emerged to facilitate
the sharing and migration of software by defining immutable, reusable
execution environments.

@@

>>>>

\begin{abstract}
We present \boutiques, a system to automatically publish, integrate
and execute applications across computational platforms. \boutiques
applications are installed through software containers described in a
rich and flexible JSON language. A set of core tools facilitate the
construction, validation, import, execution, and publishing of
applications. \boutiques is currently supported by several distinct virtual
research platforms, and it has been used to describe dozens of
applications in the neuroinformatics domain. We expect \boutiques to
improve the quality of application integration in computational
platforms, to reduce redundancy of effort, to contribute to computational
reproducibility, and to foster Open Science.
\end{abstract}

@@

Computational platforms such as web services, portals, scientific
gateways, workflow engines and virtual research environments commonly
integrate third-party applications to enable various types of data
processing. Applications, however, are often manually and
repeatedly integrated whereas automating and
sharing this effort would improve computational
reproducibility~\cite{peng2011reproducible,Stodden1240} and contribute
to Open Science. Meanwhile, container systems such as
Docker\footnote{\url{https://www.docker.com}} and
Singularity~\cite{kurtzer2017singularity} have emerged to facilitate
the sharing and migration of software by defining immutable, reusable
execution environments.

@@

%% Application integration consists of 1)~installing the application
%%   on the target infrastructure, 2)~describing the application in a
%%   format compatible with the execution platform, and 3)~generating
%%   proper user interfaces.
